Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-19 paper/intro.tex
adding problem definition to intro

Our work is embedded in a substantial collection of tools, so it is
important to clarify the research contribution. We see the following
as the contributions of this paper:

@@

@@

\item A synthesis path from code contracts to \ckml, supported by a formal
   framework to argue correctness.

\item A formal argument that \agr\ verification of code contracts carry over
  to the resulting binaries from the \ckml\ compiler.

\item A case
  study that uses \brfcs\ to add cyber-resiliency to a non-trivial UAV
  system.
\end{compactitem}

Our approach currently applies to common cyber-vulnerabilities, such
as buffer overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service have not yet been addressed. Moreover, this work
does not introduce a new type of high-assurance component in terms of
capability; instead, our contribution is in the automated synthesis of
security-improving components from formal cyber-resilience
specifications and a means to show that the synthesis is correct. We
have not yet tried to apply {\brfcs} to problems outside the realm of
cyber-resilience; however, the notions of code and test contracts,
along with the system analysis and verified code generation facilities
promise to be useful in a wide variety of settings.

>>>>

As indicated in the preceding discussion, {\brfcs} is aimed at
addressing the lack of tool support for the the problem of enforcing
and implementing the class of \emph{cyber-resilience} system
requirements.  Our approach to the problem is embedded in a
substantial collection of tools, so it is important to clarify the
research impact. We see the following as the distinguishing
contributions of this paper:

@@

\item We provide a strong formal path connecting (A) top-level system cyber-resilience
  requirements, (B) specifications for high-assurance components
  inserted to mitigate against specific cyber-resilience problems, and
  (C) synthesis to a programming language with a verified compiler.

@@

\item A case study that demonstrates the use of \brfcs\ to add cyber-resiliency
 to a non-trivial UAV system.
\end{compactitem}

Our approach currently applies to common cyber-vulnerabilities, such
as buffer overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service have not yet been addressed. Moreover, this work
does not introduce a new type of high-assurance component in terms of
capability. Instead, our contribution is in the automated synthesis of
security-improving components from formal cyber-resilience
specifications, paired with a verification showing that the
synthesized implementation is correct. We have not yet tried to apply
{\brfcs} to problems outside the realm of cyber-resilience; however,
the notions of code and test contracts, along with the system analysis
and verified code generation facilities promise to be useful in a wide
variety of settings.
